## `neonTerms`
This is a package that will manage data about NEON's internal data product structures

### Quick start


```{r}
#install.packages("devtools")
#library(devtools)
#install_github("NEONdps/neonTerms")
library(neonTerms)
library(RSQLite)
options(stringsAsFactors = F)
```



### Create and set a database in options

First thing you can do is create a database.  Setting it in options makes your life a bit easier.

```{r}
createDB("test.sqlite")
db <- "test.sqlite"
options(termDB = "test.sqlite")
```


### Load in data from csv's

Next load data into CSV's

```{r}

dpd <- read.csv("testdata/dpd.csv")
space <- read.csv("testdata/spatial.csv")
temporal <- read.csv("testdata/temporal.csv")
datapub <- read.csv("testdata/mam_datain_test.csv")
genIS <- read.csv("testdata/genericIS_L1.csv")

## Add rev numbers

dpd$rev <- 1
```

Finally you can  add data to the the database.  We'll input the data publication workooks to create table definitions.
```{r}
addDPD(dpd)
addTempRes(temporal)
addSpRes(space)
inputDataPub(datapub,db)
inputDataPub(genIS,db)

## I input a generic table, so we can make extra linkages by adding a new entry to the table description table
toAdd <- data.frame(c("NEON.DOM.SIT.DP1.00002","NEON.DOM.SIT.DP1.00003"))
toAdd <- cbind(c(3,3),toAdd)
colnames(toAdd) <- c("tableID","dpID")
addTDPL(toAdd)
```


### Retrieve data

Data can be accessed via data product numbers,  Once data product numbers have been fully extracted you can easily generate a full suite of unique field numbers
```{r}
out <- qFull("NEON.DOM.SIT.DP1.00002",db)
### Generate full numbers
genFieldUID(out,db)
```

